### 2016-05-25 paper/paper.tex
spell check

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle, such as in Bitcoin, miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retreive an assigned
portion of the file.

@@

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward and the right to specify what new, valid transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the Merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, therby
changing the Merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

@@

where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
$output\_script$ is the SHA256 hash of the output script the payee wants to collect the
payment with, and $N$ is a 32-byte random nonce.  The client then makes connections to the
specified victim domain until it gets a response that meets the target
difficulty specified by the PAY\_TO\_DDOS transaction, i.e. the hash of the key exchange 
parameters, signature, and nonce are less than the target hash value.

@@

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their priveleged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
and sufficiently difficult proof-of-work
would indicate to the bounty provider that the target is claiming its bounty.

@@

DDoSCoin adjusts diffuculty for a given domain by looking at the past
BLOCK\_ADJUST blocks, and counting the number of blocks mined against
the given domain. This ratio is compared to the expected ratio based on the
current size of the victim list. If more blocks were mined than expected, the
difficulty for this domain is increased. Similarly, if fewer blocks were mined,
the difficulty for the domain is decreased.
This mechanism allows target domains that somehow become more
difficult to reach to quickly return to a more appropriate difficulty, without
having to wait for many blocks mined at the high difficulty.

@@

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level. These are similar to the incentives for PAY\_TO\_DDOS 
transactions, mentioned in Section~\ref{sec:pay-to-ddos}.

@@

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
malicousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
but negatively impacts society as a whole.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
to the currency 
when miners have different bandwidths to that given endpoint. The extreme of 
having a different bandwidth is being the target, and having the private key 
for the site. Having this priveleged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowlege this work introduces an idea that could be used to incentivize 
malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin.
We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
beyond just DDoSCoin.

@@

Websites could also attempt to thwart DDoSCoin by participating in the mining
themselves. Because the victim website will have local access to its private
key, they will have an advantage over remote clients. With this advantage, the
victim might be able to mine enough DDoSCoins to mint a proof-of-stake block
that removes itself from the list, or raise the difficulty of mining a block
high enough that a remote miner has a negligable chance of suceeding.

>>>>

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle, such as in Bitcoin, miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retrieve an assigned
portion of the file.

@@

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward and the right to specify what new, valid transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the Merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, thereby
changing the Merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

@@

Where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
$output\_script$ is the SHA256 hash of the output script the payee wants to collect the
payment with, and $N$ is a 32-byte random nonce.  The client then makes connections to the
specified victim domain until it gets a response that meets the target
difficulty specified by the PAY\_TO\_DDOS transaction, i.e. the hash of the key exchange 
parameters, signature, and nonce are less than the target hash value.

@@

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their privileged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
and sufficiently difficult proof-of-work
would indicate to the bounty provider that the target is claiming its bounty.

@@

DDoSCoin adjusts difficulty for a given domain by looking at the past
BLOCK\_ADJUST blocks, and counting the number of blocks mined against
the given domain. This ratio is compared to the expected ratio based on the
current size of the victim list. If more blocks were mined than expected, the
difficulty for this domain is increased. Similarly, if fewer blocks were mined,
the difficulty for the domain is decreased.
This mechanism allows target domains that somehow become more
difficult to reach to quickly return to a more appropriate difficulty, without
having to wait for many blocks mined at the high difficulty.

@@

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be ineffective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level. These are similar to the incentives for PAY\_TO\_DDOS 
transactions, mentioned in Section~\ref{sec:pay-to-ddos}.

@@

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
maliciousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
but negatively impacts society as a whole.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
to the currency 
when miners have different bandwidths to that given endpoint. The extreme of 
having a different bandwidth is being the target, and having the private key 
for the site. Having this privileged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowledge this work introduces an idea that could be used to incentivize 
malicious behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin.
We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
beyond just DDoSCoin.

@@

Websites could also attempt to thwart DDoSCoin by participating in the mining
themselves. Because the victim website will have local access to its private
key, they will have an advantage over remote clients. With this advantage, the
victim might be able to mine enough DDoSCoins to mint a proof-of-stake block
that removes itself from the list, or raise the difficulty of mining a block
high enough that a remote miner has a negligible chance of succeeding.
